NoTitle

### 2017-06-12 Aplas17/sections/Formalization.tex

\begin{figure*}[htbp]
\begin{mathpar}
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	\tsuperinvk \\
	\tnew \\
	\tmethod \\
	\tintf
\end{mathpar}
\caption{Typing rules.}\label{fig:typingrules}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\begin{mathpar}
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	\tsuperinvk \\
	\tnew \\
	\tmethod \\
	\tintf
\end{mathpar}
\caption{Typing rules.}\label{fig:typingrules}
\end{figure*}
\bruno{Path invocation subsumes regular invocation. In other words:
e0.m(e) = e0.I::m(e) when the type of e0 is I.}
\bruno{Last time I met I told you that the typing of ``this'' is
  wrong, and this is not yet fixed. I've also told you to make all
figures at the top. In T-Method, \Gamma shows up out of nowhere.
}
\bruno{Rule for new is wrong! It says that a new expression that
  creates a class with any name (even if the class does not exist) 
is valid. The paper is not even following the rules of FJ.}
